Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-02 papers/B1555_EdgeOn/B1555_letter.tex
Reorder/rewrite on Discussion[incomplete]

\simona{It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
\simona{Indeed,} little perturbations in the gravitational potential are sufficent to bring flux ratio anomalies in strong lensed systems. 
\simona{Moreover, unlike in the optical or infrared,} in the radio band, lensed images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
\simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}. While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}. Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.}

@@

\section{Lens Modelling}
To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. The discrepency between numerical simulations and observations within the Local Universe gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples. Lensing shows a promising potential on substructure detection beyond the Local Group. The main reason is that the gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.

Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref). Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey. Radio data provides reliable positions and fluxes of source for constraint and modelling because it avoids the problem of severe extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The lack of knowledge about lens galaxy, e.g. modelling with radio data alnog, may lead to an improper lens model.

The idea of detecting substructures with flux ratio anomalies assumes that lens galaxy has completely smooth gravitational potential. Thus the perturbation is considered to be from faint satellite galaxy or ``dark'' subhalo. Numerical simulations have examined this approach with unkown systems. In \citet{Xu14}, only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos. The rest of them are only few percent likely or very unlikely to have their flux anomalies due to substructure, including B1555+375. Their results support that even using radio data, there are other possible reasons could cause flux anomalies. The answer to this concern may be explained by the high resolution IR imaging. In the SHARP K-band imaging of B1555+375, an edge-on disk lies across between the positions of radio merging double A \& B.

@@

Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. The radio and narrow band observations are the best approaches to obtain accurate flux ratio data. However, optical and infrared imaging can provide more information on the structure of lens galaxy. With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

\simona{It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
\simona{Indeed,} little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
\simona{Moreover, unlike in the optical or infrared,} in the radio band, lensed images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
\simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}. While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}. Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.}

@@

\section{Lens Modelling}
To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this new information from A/O image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. The discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe. Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites. This makes gravitational lensing a powerful tool for the detection of substructures. The gravitational perturbation from substructure is sufficient to bring flux ratio anomaly in strong lensing systems. These perturbations reflect the total mass of substructures. Give directly measurement of mass function and avoid assumptions on how baryonic matter distributes with dark matter.

The discussion on substructure searching in strong lensing systems are mostly done by multiple images of lensed quasar. Until now there are a dozen(?) flux anomalous lensed quasars and the number must increase in the future surveys. With the assumption of smooth gravitational potential from lens galaxy, flux ratio anomalies are brought by substructure perturbations. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomalies, including B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP K-band image, which an edge-on disk lies across between the positions of radio merging double A \& B. 
more complicated structure

@@

Thus radio data provides reliable information for constraint and modelling because it avoids the problem of dust extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The lack of knowledge about lens galaxy, e.g. modelling with radio data alnog, may lead to an improper lens model.
Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. The radio and narrow band observations are the best approaches to obtain accurate flux ratio data. However, optical and infrared imaging can provide more information on the structure of lens galaxy. With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
